Visualizations for the manuscript

### 2022-04-28 metanalysis_visualization/manuscript_Figures.Rmd
add the saving figures for the manuscript

ggplot(bootstrapped_fitted_all, aes(x = time_p, y = predicted, group = interaction(iteration, period))) +
  facet_wrap("plotsLabel", scales = "free_y", labeller = label_wrap_gen(width = 35,multi_line = TRUE)) +
  geom_line(aes(color = period),
            alpha = 0.03) +
  geom_line(data = quantile_bootstrapped_fitted_all,
            aes(y = value, group = interaction(quantiles, period)),
            linetype = "dashed") +
  geom_line(data = quantile_bootstrapped_fitted_all[quantile_bootstrapped_fitted_all$quantiles == "50%", ],
            aes(y = value, group = period)) +
  geom_point(data = patient_count_psy_period_psy_all,
             aes(y = percentage, group=NULL),
             alpha = 0.5) +
  scale_colour_manual(values = cbPalette) +
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0))+
  guides(color = guide_legend(override.aes = list(alpha = 1))) +
  geom_label(data = plot_annotations_df, 
             aes(label=label), 
            x = -Inf,
            y = +Inf,
            hjust = 0,
            vjust = 1,
            size = 4,
            inherit.aes = FALSE) +
  labs(title = "Interrupted Time Series Analysis: Percentage of patients with psychiatric conditions",
       subtitle = "Parametric bootstrap estimation: (10000 iterations)",
       x = "Calendar dates",
       y = "Percentage",
       color = "Period") +
  theme(strip.text = element_text(size = 10),
        axis.text.x=element_text(angle = 45, hjust=1, size = 8),
        axis.text.y = element_text(size = 8), 
        axis.title.x = element_text(size = 8),
        axis.title.y = element_text(size = 8),
        title = element_text(size = 14),
        plot.subtitle = element_text(size = 12, face = "italic")) 
ggsave("figure1_boostrapped_all.png", height = 20, width = 45, units = "cm")
```

@@

```{r}
# Random effect
trends_siteid <- trends_siteid %>%
  left_join( country_map )
model_meta_siteid <- metafor::rma(yi = observed, 
                                  vi = var_boot,
                                  measure = "MN",
                                  method = "DL",
                                  data = trends_siteid)

metafor::forest(model_meta_siteid,
                slab = trends_siteid$plotsLabel,
                plim = c(1, NA),
                order = "obs",
                cex=0.7,
                showweights = TRUE,
                header="Sites",
                mlab="Overall periods' slope differences")
ggsave("figure2A_metaanalysis_persite.png", height = 20, width = 45, units = "cm")

@@

```{r}
trends_country <- trends_siteid %>% 
  group_by(country) %>% 
  group_modify(.f = function(x, ...) {
    as.data.frame(
      predict(rma(yi = observed, 
                vi = var_boot,
                measure = "MN",
                method = "DL",
                data = x))
    )
  },
  .keep = TRUE)

@@

forest(model_meta_country, 
       slab = trends_country$country,
       plim = c(1, NA),
       order = "obs", 
       showweights = TRUE,
       header = "Countries",
       mlab = "Overall periods' slope differences")
ggsave("figure2B_metaanalysis_country.png", height = 20, width = 45, units = "cm")

@@

```{r bootstrap_plot}
ggplot(bootstrapped_fitted_sex, aes(x = time_p, y = predicted, group = interaction(iteration, period, sex))) +
  # facet_wrap("plotsLabel", scales = "free_y", labeller = label_wrap_gen(width = 35,multi_line = TRUE)) +
  geom_line(aes(color = interaction(period, sex)),
            alpha = 0.03) +
  geom_line(data = quantile_bootstrapped_fitted_sex,
            aes(y = value, group = interaction(quantiles, period, sex)),
            linetype = "dashed") +
  geom_line(data = quantile_bootstrapped_fitted_sex[quantile_bootstrapped_fitted_sex$quantiles == "50%", ],
            aes(y = value, group = interaction(period, sex))) +
  geom_point(data = patients_hospitalized_agg_sex_total,
             aes(y = percentage, group=sex, color = interaction(period, sex)),
             alpha = 1) +
  scale_color_brewer(palette = "Paired") +
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0))+
  # scale_colour_manual(values = c("#A6CEE3", "#1F78B4", "#B2DF8A", "#33A02C")) +
  guides(color = guide_legend(override.aes = list(alpha = 1))) +
  geom_label(data = plot_annotations_sex_df,
             aes(label=label),
            x = -Inf,
            y = +Inf,
            hjust = 0,
            vjust = 1,
            size = 4,
            inherit.aes = FALSE) +
  labs(title = "Interrupted Time Series Analysis: Percentage of patients with psychiatric conditions",
  subtitle = "Parametric bootstrap estimation: (10000 iterations)",
       x = "Calendar dates",
       y = "Percentage",
       color = "Period") +
  theme(strip.text = element_text(size = 10),
        axis.text.x=element_text(angle = 45, hjust=1, size = 8),
        axis.text.y = element_text(size = 8),
        axis.title.x = element_text(size = 8),
        axis.title.y = element_text(size = 8),
        title = element_text(size = 14),
  plot.subtitle = element_text(size = 12, face = "italic"))
ggsave("figure4_ITS_sex.png", height = 20, width = 45, units = "cm")

@@

ggplot(bootstrapped_fitted_disorder,
       aes(x = time_p, y = predicted, group = interaction(iteration, period))) +
  facet_wrap("disorder_group",
             scales = "free_y",
             labeller = label_wrap_gen(width = 35,multi_line = TRUE)) +
  geom_line(aes(color = period),
            alpha = 0.03) +
  geom_line(data = quantile_bootstrapped_fitted_disorder,
            aes(y = value, group = interaction(quantiles, period)),
            linetype = "dashed") +
  geom_line(data = quantile_bootstrapped_fitted_disorder[quantile_bootstrapped_fitted_disorder$quantiles == "50%", ],
            aes(y = value, group = period)) +
  geom_point(data = filter(perc_disorder_group_total,
                           disorder_group %in% disorders_to_select),
             aes(y = percentage, group=NULL),
             alpha = 0.5) +
  scale_colour_manual(values = cbPalette) +
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0))+
  guides(color = guide_legend(override.aes = list(alpha = 1))) +
  geom_label(data = plot_annotations_disorder_df, 
             aes(label=label), 
            x = -Inf,
            y = +Inf,
            hjust = 0,
            vjust = 1,
            size = 4,
            inherit.aes = FALSE) +
  labs(title = "Interrupted Time Series Analysis: Percentage of patients with psychiatric conditions",
       subtitle = "Parametric bootstrap estimation: (10000 iterations)",
       x = "Calendar dates",
       y = "Percentage",
       color = "Period") +
  theme(strip.text = element_text(size = 10),
        axis.text.x=element_text(angle = 45, hjust=1, size = 8),
        axis.text.y = element_text(size = 8), 
        axis.title.x = element_text(size = 8),
        axis.title.y = element_text(size = 8),
        title = element_text(size = 14),
        plot.subtitle = element_text(size = 8, face = "italic")) 
ggsave("figure3_boostrapped_disorders.png", height = 15, width = 35, units = "cm")

@@

fig
ggsave("figure_supp3_counts_disorder.png", height = 20, width = 45, units = "cm")

#### facet wrap in 3 groups based on %
### most prevalent
perc_disorder_group_total %>%
  filter(disorder_group %in% c("Anxiety Disorders", "Depressive Disorders", "Suicide or Self-Injury" ))  %>%
  ggplot( aes( x= as.Date( time_p ), y = percentage, group = country )) +
  facet_wrap( ~ disorder_group ) +
  geom_line( aes(color = country )) +
  geom_point( aes( color = country )) +
  geom_vline(xintercept = as.Date(pandemic_start_date), linetype = "dashed")+
  labs(x ="", y = "percentage of patients (%)")+
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0))+
  theme(axis.text.x=element_text(angle = 45, hjust=1, size = 6),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.border = element_rect(colour = "black", fill = NA)) +
  scale_color_manual( values = cbPalette )

#medium prevalent
perc_disorder_group_total %>%
  filter(disorder_group %in% c("Trauma and Stressor-Related Disorders", "Mental Health Symptom", "Disruptive, Impulse Control and Conduct Disorders", 
                               "Feeding and Eating Disorders"))  %>%
  ggplot( aes( x= as.Date( time_p ), y = percentage, group = country )) +
  facet_wrap( ~ disorder_group ) +
  geom_line( aes(color = country )) +
  geom_point( aes( color = country )) +
  geom_vline(xintercept = as.Date(pandemic_start_date), linetype = "dashed")+
  labs(x ="", y = "percentage of patients (%)")+
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0))+
  theme(axis.text.x=element_text(angle = 45, hjust=1, size = 6),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.border = element_rect(colour = "black", fill = NA)) +
  scale_color_manual( values = cbPalette )

#low prevalent
perc_disorder_group_total %>%
  filter(disorder_group %in% c("Miscellaneous", "Substance-Related and Addictive Disorders", 
                               "Personality Disorders", "Bipolar and Related Disorders", "Sleep-Wake Disorders", 
                               "Schizophrenia Spectrum and Other Psychotic Disorders", "Somatic Symptom and Related Disorders", 
                               "Obsessive-Compulsive and Related Disorders", "Dissociative Disorders" ))  %>%
  ggplot( aes( x= as.Date( time_p ), y = percentage, group = country )) +
  facet_wrap( ~ disorder_group ) +
  geom_line( aes(color = country )) +
  geom_point( aes( color = country )) +
  geom_vline(xintercept = as.Date(pandemic_start_date), linetype = "dashed")+
  labs(x ="", y = "percentage of patients (%)")+
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0))+
  theme(axis.text.x=element_text(angle = 45, hjust=1, size = 6),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.border = element_rect(colour = "black", fill = NA)) +
  scale_color_manual( values = cbPalette )

perc_disorder_group_total %>%
  filter(disorder_group %in% c("Anxiety Disorders", "Depressive Disorders", "Suicide or Self-Injury" ))  %>%
  ggplot( aes( x= as.Date( time_p ), y = percentage, group = country )) +
  facet_wrap( ~ disorder_group ) +
  geom_line( aes(color = country )) +
  geom_point( aes( color = country )) +
  geom_vline(xintercept = as.Date(pandemic_start_date), linetype = "dashed") +
  labs(x ="", y = "percentage of patients (%)")+
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0)) +
  scale_color_manual( values = cbPalette ) + 
  theme(axis.text.x=element_text(angle = 45, hjust=1, size = 6), 
        strip.text = element_text(size = 10, face = "bold"),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(), strip.background = element_blank(),
        panel.border = element_rect(colour = "black", fill = NA), 
        legend.position="bottom")

perc_disorder_group_total %>%
  filter( disorder_group %in% c("Anxiety Disorders", "Depressive Disorders", "Suicide or Self-Injury", 
  "Mental Health Symptoms", "Feeding and Eating Disorders" )) %>%
  ggplot( aes( x= as.Date( time_p ), y = percentage, group = country )) +
  geom_line( aes(linetype = country, color = country )) +
  geom_point( aes( shape= country, color = country )) +
  #scale_y_continuous(breaks = seq(0, 30, by = 5)) +
  facet_wrap2("disorder_group", axes = "all", scales ="free") + 
  geom_vline(xintercept = as.Date(pandemic_start_date), linetype = "dashed") +
  labs(x ="", y = "percentage of patients (%)")+
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0)) +
  scale_color_manual( values = cbPalette ) + 
  theme(axis.text.x=element_text(angle = 45, hjust=1, size = 6), 
        strip.text = element_text(size = 10, face = "bold"),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(), strip.background = element_blank(),
        panel.border = element_rect(colour = "black", fill = NA), 
        legend.position="bottom")

@@

### By site
```{r}
head(patient_count_psy_period_psy_all)
sites <- unique( patient_count_psy_period_psy_all$siteid )
source("../metanalysis_visualization/time_series_analysis_plotting.R")
p <- list()

@@

g <- do.call(grid.arrange,p)
ggsave("its_seasonality_site.png",g, height = 20, width = 32, units = "cm")

@@

counts_agg2 %>% ggplot( aes( x= as.Date( time_p ), y = value, group= group )) +
  geom_point( aes( shape= group, color = group )) +
  geom_vline(xintercept = as.Date(pandemic_start_date), linetype = "dashed") +
  labs(x ="", y = "number of patients")+
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0)) +
  scale_color_manual( values = cbPalette ) + 
  theme(axis.text.x=element_text(angle = 45, hjust=1, size = 6), 
        strip.text = element_text(size = 10, face = "bold"),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(), strip.background = element_blank(),
        panel.border = element_rect(colour = "black", fill = NA), 
        legend.position="bottom")
ggsave("figure_supp1B_counts_all.png",counts_plot, height = 20, width = 32, units = "cm")

>>>>

ggplot(bootstrapped_fitted_all, aes(x = time_p, y = predicted, group = interaction(iteration, period))) +
  facet_wrap("plotsLabel", scales = "free_y", labeller = label_wrap_gen(width = 35,multi_line = TRUE)) +
  geom_line(aes(color = period),
            alpha = 0.03) +
  geom_line(data = quantile_bootstrapped_fitted_all,
            aes(y = value, group = interaction(quantiles, period)),
            linetype = "dashed") +
  geom_line(data = quantile_bootstrapped_fitted_all[quantile_bootstrapped_fitted_all$quantiles == "50%", ],
            aes(y = value, group = period)) +
  geom_point(data = patient_count_psy_period_psy_all,
             aes(y = percentage, group=NULL),
             alpha = 0.5) +
  scale_colour_manual(values = cbPalette) +
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0))+
  guides(color = guide_legend(override.aes = list(alpha = 1))) +
  geom_label(data = plot_annotations_df, 
             aes(label=label), 
            x = -Inf,
            y = +Inf,
            hjust = 0,
            vjust = 1,
            size = 4,
            inherit.aes = FALSE) +
  labs(title = "Interrupted Time Series Analysis: Percentage of patients with psychiatric conditions",
       subtitle = "Parametric bootstrap estimation: (10000 iterations)",
       x = "Calendar dates",
       y = "Percentage",
       color = "Period") +
  theme(strip.text = element_text(size = 14),
        axis.text.x=element_text(angle = 45, hjust=1, size = 8),
        axis.text.y = element_text(size = 8), 
        axis.title.x = element_text(size = 8),
        axis.title.y = element_text(size = 8),
        title = element_text(size = 14),
        plot.subtitle = element_text(size = 12, face = "italic"), 
        legend.position="bottom") 
ggsave("figure1_boostrapped_all.png", height = 20, width = 45, units = "cm")
```

@@

```{r}
# Random effect
png(file='./figure2A_metaanalysis_persite.png')

trends_siteid <- trends_siteid %>%
  left_join( country_map )
model_meta_siteid <- metafor::rma(yi = observed, 
                                  vi = var_boot,
                                  measure = "MN",
                                  method = "DL",
                                  data = trends_siteid)

metafor::forest(model_meta_siteid,
                slab = trends_siteid$plotsLabel,
                plim = c(1, NA),
                order = "obs",
                cex=0.7,
                showweights = TRUE,
                header="Sites",
                mlab="Overall periods' slope differences")
dev.off()
#ggsave("figure2A_metaanalysis_persite.png", height = 20, width = 45, units = "cm")

@@

```{r}
png(file='figure2B_metaanalysis_country.png')

trends_country <- trends_siteid %>% 
  group_by(country) %>% 
  group_modify(.f = function(x, ...) {
    as.data.frame(
      predict(rma(yi = observed, 
                vi = var_boot,
                measure = "MN",
                method = "DL",
                data = x))
    )
  },
  .keep = TRUE)

@@

forest(model_meta_country, 
       slab = trends_country$country,
       plim = c(1, NA),
       order = "obs", 
       showweights = TRUE,
       header = "Countries",
       mlab = "Overall periods' slope differences")
dev.off()
```

@@

```{r bootstrap_plot}
ggplot(bootstrapped_fitted_sex, aes(x = time_p, y = predicted, group = interaction(iteration, period, sex))) +
  # facet_wrap("plotsLabel", scales = "free_y", labeller = label_wrap_gen(width = 35,multi_line = TRUE)) +
  geom_line(aes(color = interaction(period, sex)),
            alpha = 0.03) +
  geom_line(data = quantile_bootstrapped_fitted_sex,
            aes(y = value, group = interaction(quantiles, period, sex)),
            linetype = "dashed") +
  geom_line(data = quantile_bootstrapped_fitted_sex[quantile_bootstrapped_fitted_sex$quantiles == "50%", ],
            aes(y = value, group = interaction(period, sex))) +
  geom_point(data = patients_hospitalized_agg_sex_total,
             aes(y = percentage, group=sex, color = interaction(period, sex)),
             alpha = 1) +
  scale_color_brewer(palette = "Paired") +
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0))+
  # scale_colour_manual(values = c("#A6CEE3", "#1F78B4", "#B2DF8A", "#33A02C")) +
  guides(color = guide_legend(override.aes = list(alpha = 1))) +
  geom_label(data = plot_annotations_sex_df,
             aes(label=label),
            x = -Inf,
            y = +Inf,
            hjust = 0,
            vjust = 1,
            size = 4,
            inherit.aes = FALSE) +
  labs(title = "Interrupted Time Series Analysis: Percentage of patients with psychiatric conditions",
  subtitle = "Parametric bootstrap estimation: (10000 iterations)",
       x = "Calendar dates",
       y = "Percentage",
       color = "Period") +
  theme(strip.text = element_text(size = 10),
        axis.text.x=element_text(angle = 45, hjust=1, size = 8),
        axis.text.y = element_text(size = 8),
        axis.title.x = element_text(size = 8),
        axis.title.y = element_text(size = 8),
        title = element_text(size = 14),
  plot.subtitle = element_text(size = 12, face = "italic"), 
  legend.position = "bottom")
ggsave("figure4_ITS_sex.png", height = 20, width = 20, units = "cm")
```

@@

ggplot(bootstrapped_fitted_disorder,
       aes(x = time_p, y = predicted, group = interaction(iteration, period))) +
  facet_wrap("disorder_group",
             scales = "free_y",
             labeller = label_wrap_gen(width = 35,multi_line = TRUE)) +
  geom_line(aes(color = period),
            alpha = 0.03) +
  geom_line(data = quantile_bootstrapped_fitted_disorder,
            aes(y = value, group = interaction(quantiles, period)),
            linetype = "dashed") +
  geom_line(data = quantile_bootstrapped_fitted_disorder[quantile_bootstrapped_fitted_disorder$quantiles == "50%", ],
            aes(y = value, group = period)) +
  geom_point(data = filter(perc_disorder_group_total,
                           disorder_group %in% disorders_to_select),
             aes(y = percentage, group=NULL),
             alpha = 0.5) +
  scale_colour_manual(values = cbPalette) +
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0))+
  guides(color = guide_legend(override.aes = list(alpha = 1))) +
  geom_label(data = plot_annotations_disorder_df, 
             aes(label=label), 
            x = -Inf,
            y = +Inf,
            hjust = 0,
            vjust = 1,
            size = 4,
            inherit.aes = FALSE) +
  labs(title = "Interrupted Time Series Analysis: Percentage of patients with psychiatric conditions",
       subtitle = "Parametric bootstrap estimation: (10000 iterations)",
       x = "Calendar dates",
       y = "Percentage",
       color = "Period") +
  theme(strip.text = element_text(size = 10),
        axis.text.x=element_text(angle = 45, hjust=1, size = 8),
        axis.text.y = element_text(size = 8), 
        axis.title.x = element_text(size = 8),
        axis.title.y = element_text(size = 8),
        title = element_text(size = 14),
        plot.subtitle = element_text(size = 8, face = "italic"), 
        legend.position = "bottom") 
ggsave("figure3_boostrapped_disorders.png", height = 15, width = 25, units = "cm")

@@

fig
#plotly::orca(fig, file = "figure_supp3_counts_disorder.png")
```

@@

### By site
```{r}
sites <- unique( patient_count_psy_period_psy_all$siteid )
source("../metanalysis_visualization/time_series_analysis_plotting.R")
p <- list()

@@

g <- do.call(grid.arrange,p)
#ggsave("its_seasonality_site.png",g, height = 20, width = 32, units = "cm")

@@

counts_agg2plot <- counts_agg2 %>% ggplot( aes( x= as.Date( time_p ), y = value, group= group )) +
  geom_point( aes( shape= group, color = group )) +
  geom_vline(xintercept = as.Date(pandemic_start_date), linetype = "dashed") +
  labs(x ="", y = "number of patients")+
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0)) +
  scale_color_manual( values = cbPalette ) + 
  theme(axis.text.x=element_text(angle = 45, hjust=1, size = 6), 
        strip.text = element_text(size = 10, face = "bold"),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(), strip.background = element_blank(),
        panel.border = element_rect(colour = "black", fill = NA), 
        legend.position="bottom")
counts_agg2plot
ggsave("figure_supp1B_counts_all.png",counts_agg2plot, height = 20, width = 32, units = "cm")
